Paper Two Summary

### 2015-09-09 hw/read/2/summary.tex
Added another possible improvement to paper 2

\section*{Possible Improvements}
\begin{itemize}
\item In the Introduction section, the authors reference a paper published
in 1989 to cite a percentage of effort spent on testing. Is there
a more recent paper the authors could have chosen to cite? If not,
why quote a figure that is 26 years old and quite possibly outdated?
\item While the way that the authors combined data in an attempt to consolidate
it to a smaller number of tables was very clever, it produces tables
that are very difficult to interpret. They have split the data into
a standard set of stats (mean, median, Q1, Q3) on half of the table
and then created a diagonal split on the other half of the table into
two sets of data, one for effect size and the other for the Wilcoxon
test data. It seems that they had so much data to report that it would
have been impossible to report it in the space they had available
without this type of table, but perhaps some further graphical representation
would have been preferable with an appendix of the tables and data
sets split out into more easily decipherable tables.
\end{itemize}

>>>>

\section*{Possible Improvements}
\begin{itemize}
\item In the Introduction section, the authors reference a paper published
in 1989 to cite a percentage of effort spent on testing. Is there
a more recent paper the authors could have chosen to cite? If not,
why quote a figure that is 26 years old and quite possibly outdated? 
\item While the way that the authors combined data in an attempt to consolidate
it to a smaller number of tables was very clever, it produces tables
that are very difficult to interpret. They have split the data into
a standard set of stats (mean, median, Q1, Q3) on half of the table
and then created a diagonal split on the other half of the table into
two sets of data, one for effect size and the other for the Wilcoxon
test data. It seems that they had so much data to report that it would
have been impossible to report it in the space they had available
without this type of table, but perhaps some further graphical representation
would have been preferable with an appendix of the tables and data
sets split out into more easily decipherable tables. 
\item The authors mentioned that one threat to the validity of the study
was that the cost of making the measures available and collecting
them was not accounted for. It seems that such calcuations should
be taken into account. Additionally, they note that the Process metric
set has a high cost of data reporting and collection but was found
to be the most cost-effective. It is hard to say if Process is indeed
the most cost-effective, since all cost measures were not taken into
consideration. A future study should include as many cost factors
as possible when determining the cost-effectiveness of a particular
method or metric.
\end{itemize}
